Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-01-09 _tex/paper2.tex
Built site for gh-pages

SCMs and DAGs offer three key advantages for modeling causal structures.
First, they enable researchers to represent causal relations in a
non-parametric and fully interactive manner. This feature allows for
feasible ACE identification strategies without specifying the data type
or the nature of the functional dependence among variables
\citep{Morgan_et_al_2014}. Second, regardless of complexity, they can
represent a wide range of causal structures using only five fundamental
building blocks \citep{Neal_2020, McElreath_2020}. This feature allows
researchers to decompose complex structures, facilitating their analysis
by focusing on the causal assumptions associated with each building
block \citep{McElreath_2020}. Finally, they help to formalize (causal)
theoretical models into (probabilistic) statistical models for
identification purposes \citep{McElreath_2020} \citep{McElreath_2020}.

@@

\caption{\label{fig-example}Plausible causal structure of the example.}

>>>>

SCMs and DAGs offer two key advantages for modeling causal structures.
First, they enable researchers to represent causal relations in a
non-parametric and fully interactive manner. This feature allows for
feasible ACE identification strategies without specifying the data type
or the nature of the functional dependence among variables
\citep{Morgan_et_al_2014}. Second, regardless of complexity, they can
represent a wide range of causal structures using only five fundamental
building blocks \citep{Neal_2020, McElreath_2020}. This feature allows
researchers to decompose complex structures, facilitating their analysis
by focusing on the causal assumptions associated with each building
block \citep{McElreath_2020}.

@@

\caption{\label{fig-example}Plausible causal structure for the example.}
